Towards Transparency and Open Science

### 2023-02-01 manuscript.Rmd
no big fan of the phrase "to lay open" in general
for example in line 200 one could also use something like "emphasize"/"highlight"/"point out"
lay open sound to die like more of a German phrase that has been translated
changed "motivates" for "promotes"

The need for transparency is closely tied to the use of induction in the empirical test of a theory.
There has been a long and vigorous debate about what it means to test a theory empirically [@popperLogicScientificDiscovery2002, Ch.\ 5 Experience as a Method].
I do not attempt to rehash the debate about what constitutes an empirical test.
However, I aim to lay open the role of transparency in two frameworks that lend themselves to investigate induction.
The first framework motivates transparency when an empirical test aims to evaluate a theory's verisimilitude ("closeness to truth").
The second framework motivates transparency under a science that wants to select a theory according to its expected predictive performance.

>>>>

The need for transparency is closely tied to the use of induction in the empirical test of a theory.
There has been a long and vigorous debate about what it means to test a theory empirically [@popperLogicScientificDiscovery2002, Ch.\ 5 Experience as a Method].
I do not attempt to rehash the debate about what constitutes an empirical test.
However, I aim to emphasize the role of transparency in two frameworks that lend themselves to investigate induction.
The first framework promotes transparency when an empirical test aims to evaluate a theory's verisimilitude ("closeness to truth").
The second framework promotes transparency under a science that wants to select a theory according to its expected predictive performance.
